
\documentclass[letterpaper,11pt]{article}

%-----------------------------------------------------------
%Margin setup

\setlength{\voffset}{0.1in}
\setlength{\paperwidth}{8.5in}
\setlength{\paperheight}{11in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\textheight}{11in}
\setlength{\textheight}{9.5in}
\setlength{\topmargin}{-0.35in}
\setlength{\textwidth}{7in}
\setlength{\topskip}{0in}
\setlength{\oddsidemargin}{-0.35in}
\setlength{\evensidemargin}{-0.35in}
%-----------------------------------------------------------
%\usepackage{fullpage}
%\textheight=9.0in
\pagestyle{empty}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item[--] #1 \vspace{-4pt}}
\newcommand{\resheading}[1]{{\large \parashade[.9]{sharpcorners}{\textbf{#1 \vphantom{p\^{E}}}}}}
\newcommand{\ressubheading}[4] {
\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
	\textbf{#1} & \textit{#2} \\
	\textit{#3} & \textit{#4}\\
\end{tabular*}\vspace{-6pt}}

\newcommand{\ressubheadingtwo}[2] {
\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
	\textbf{#1} & \textit{#2} \\
\end{tabular*}\vspace{-6pt}}

\newcommand{\ressubhead}[2] {
\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
	\textbf{#1} & \textit{#2} \\
\vspace{0.01in}
\end{tabular*}\vspace{-6pt}}

\usepackage{xcolor}
\usepackage[colorlinks = true, 
	linkcolor = blue,
	urlcolor  = blue,
	citecolor = blue,
	anchorcolor = blue]{hyperref}

\newcommand{\MYhref}[3][blue]{\href{#2}{\color{#1}{#3}}}%

%-----------------------------------------------------------


\begin{document}

\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Skanda Koppula}  & \href{mailto:skoppula@mit.edu}{\nolinkurl{skoppula@mit.edu}}\\
  550 Memorial Drive &  \href{http://skoppula.github.io}{\nolinkurl{skoppula.github.io}}\\
	Cambridge, MA 02139 & 1.412.259.3123\\
\end{tabular*}
\\

\vspace{0.05in}

%\resheading{Education}
\ressubheading{Massachusetts Institute of Technology}{}{\vspace{4mm}Masters of Engineering, BSc, Computer Systems,  MEng GPA: 5.0/5.0}{Sept. 2013 - Expected February 2018}
\textit{Relevant courses:} Hardware Architecture for Deep Learning, Computer and Network Security, Cryptography and Cryptoanalysis, Compilers, Operating Systems, Constructive Computer Architecture, Computer Networks, Bayesian Inference, Machine Learning

\vspace{0.05in}

\large \textbf{Work Experience\vspace{1mm}} \normalsize

	\ressubheadingtwo{Google Search, Software Research Intern}{June 2017 - September 2017}
	\begin{itemize}
            \resitem{Tested decomposition methods to improve cross-domain adaptability of recurrent neural language models (e.g. character LSTM/RNNs).}
            \resitem{Developed new method to visualize memory of recurrent neural networks, as applied to character language models and end-to-end speech recognition systems.}
            \resitem{Paper under review for 2018 IEEE Conference on Acoustics and Signal Processing. \url{https://people.csail.mit.edu/skoppula/papers/memory-signatures.pdf} }
	\end{itemize}

	\ressubheadingtwo{Yahoo Login Abuse, Software Engineering Intern}{June 2016 - Aug. 2016}
	\begin{itemize}
            \resitem{Prototyped neural network to classify account registration and login events on Yahoo services as spam. Demonstrated a 6\% improvement in classifier's equal error rate from prior system.}
            \resitem{Deployed a multi-threaded data feed service to pull data hourly from Facebook ThreatExchange and thirty-one sources to update classifier of with threat intelligence. Awarded outstanding intern project bonus.}
	\end{itemize}

    \vspace{0.05in}

    \vspace{0.05in}
	\ressubheadingtwo{Square Security, Software Engineering Intern}{June 2015 - Aug. 2015}
	\begin{itemize}
            \resitem{Developed service to collect memory core crashdumps from Square card readers, symbolifing the binary contents to a human-readable source error trace.}
	\end{itemize}

    \vspace{0.05in}

\large \textbf{Research \vspace{1mm}} \normalsize
    \vspace{0.05in}

	\ressubheadingtwo{MIT Energy Efficient Circuits Group}{Sept. 2015 - Present}{}
	\begin{itemize}
            \resitem{Developed memory-efficient convolutional neural network for speaker identification. 10x size reduction and $>$100x decrease in estimated energy consumption from comparable speaker ID systems. Built custom hardware design on FPGA to evaluate ternarized speaker verification network.}
            \resitem{Prototyped software system for privacy-preserving speaker identification, obfuscating private speech data using a data representation based on locality sensitive hashing with provable security/accuracy bounds.}
            \resitem{Paper under review for 2018 IEEE Conference on Acoustics and Signal Processing. \url{https://people.csail.mit.edu/skoppula/papers/sid-ternary-nets.pdf} }
	\end{itemize}

    \ressubheadingtwo{Applying the Residue Number System to Neural Network Inference}{Fall 2017}{}
	\begin{itemize}
            \resitem{Designed and implemented procedure to use the Residue Number System (RNS) as the underlying numeric representation durng neural network inference.}
            \resitem{Implemented core required hardware blocks for RNS arithmetic with colleague. Estimated 32\% power savings reduction because of optimized RNS arithmetic hardware. Pre-print: \url{https://arxiv.org/abs/1712.04614}}
	\end{itemize}


    \ressubheadingtwo{Bayesian Inference for Detection of Illness Pre-disposition}{May 2013}{}
	\begin{itemize}
            \resitem{Applied Bayesian modeling to develop a genomic-environmental factor model to detect patients at-risk or pre-disposed to cancer, schizophrenia, and alcoholism. Published in Joint Summits of American Medical Informatics 2013: \url{https://www.ncbi.nlm.nih.gov/pubmed/24303313}}
	\end{itemize}

\large \textbf{Projects\vspace{1mm}} \normalsize

    \ressubheadingtwo{MIT Formula SAE Racecar Electronics Team, Firmware Lead}{August 2015 - Present}
    \begin{itemize}
        \resitem{Designed electronics and wrote firmware for the first open-source automotive battery management system. Orchestrates battery dis/charging state, balancing, safety checks, charging algorithms. \url{https://github.com/MITEVT/ltc-battery-controller}}
            \resitem{Trained a CNN-based controller for a driverless Formula racecar. Wrote simulator for corresponding controller model. Technical Report: \url{https://arxiv.org/abs/1708.02215}.}
    \end{itemize}

    \ressubheadingtwo{Power-Based Side-Channel Attack on ATMega328}{Nov. 2015}{}
	\begin{itemize}
            \resitem{Demonstrated extraction of an AES key from an Arduino's flash memory from chip's power traces. Implemented the Correlation Power Analysis attack. \url{people.csail.mit.edu/skoppula/papers/sidechannel.pdf}}
	\end{itemize}

    \vspace{0.05in}

\large \textbf{Skills\vspace{1mm}} \normalsize
	 \begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
         \hspace{2mm} Embedded Systems: \textbf{C}, \textbf{x86 Assembly}, \textbf{Vivado HLS}, and \textbf{Bluespec Verilog}. \\
         \hspace{2mm} Misc: \textbf{Python}, \textbf{C++}, \textbf{Java}, \textbf{Scala}, \textbf{shell scripting}, \textbf{TensorFlow/pytorch}  \\
         \hspace{2mm} Web Systems: \textbf{JAX-RS/Jetty}, \textbf{Rails/RSpec}, \textbf{Flask, Django} \\
	\end{tabular*}

\vspace{0.1in}
\large \textbf{Awards\vspace{2mm}} \normalsize
	 \begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
		 \hspace{2mm} Cisco Snort Security Scholarship Recipient & 2017\\
		 \hspace{2mm} 2nd Place North American FSAE Lincoln Electric Racing Competition (Team) & 2017\\
		 \hspace{2mm} Analog Devices Research and Innovation Scholar Award & 2016\\
		 \hspace{2mm} Fourth Place Research Poster at the 2016 MIT EECSCon Undergraduate Research Conference & 2016\\
		 \hspace{2mm} Fourth Place in Jane Street Collegiate Programmatic Trading Competition & 2015\\
		 \hspace{2mm} Qualified for AIME and USA Math Olympiad & 2013\\
		 \hspace{2mm} USA Math Talent Search Silver Division & 2012-13\\
		 \hspace{2mm} USA Biology Olympiad Semi-Finalist & 2012-13\\
		 \hspace{2mm} Google Science Fair Finalist & 2011\\
	\end{tabular*}

\vspace{0.1in}
\large \textbf{List of Publications\vspace{2mm}} \normalsize
    \begin{itemize}
            \resitem{Understanding Recurrent Neural State Using Memory Signatures. \\ Koppula, Skanda, Khe Chai Sim, and Kean Chin. \textit{Under review for 2018 IEEE Conference on Acoustics, Speech, and Signal Processing. } (2017).}
            \resitem{Energy-Efficient Speaker Identification with Low-Precision Networks. \\ Koppula, Skanda, Jim Glass, and A.P. Chandrakasan. \textit{Under review for 2018 IEEE Conference on Acoustics, Speech, and Signal Processing. } (2017).}
            \resitem{Applying the Residue Number System for Neural Network Inference. \\ Abdelhamid, Mohamed, and Skanda Koppula. \textit{Technical Report. arXiv preprint arXiv:1712.04614} (2017).}
            \resitem{Learning a CNN-based End-to-End Controller for a Formula SAE Racecar. \\ Skanda Koppula. \textit{Technical Report. arXiv preprint arXiv:1708.02215} (2017).}
            \resitem{Power-Based Side-Channel Attack for AES Key Extraction on the ATMega328 Microcontroller. Banerjee, Utsav, Lisa Ho, and Skanda Koppula.  \textit{Computer Systems Security} (2015).}
            \resitem{Robust Prediction-based Analysis for Genome-wide Association and Expression Studies. \\ Skanda Koppula, Amin Zollanvari, Ning An, and Gil Alterovitz. \textit{Proceedings of AMIA Joint Summits on Translational Science} (2013).}
    \end{itemize}
\end{document}
