
\documentclass[letterpaper,11pt]{article}

%-----------------------------------------------------------
%Margin setup

\setlength{\voffset}{0.1in}
\setlength{\paperwidth}{8.5in}
\setlength{\paperheight}{11in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\textheight}{11in}
\setlength{\textheight}{9.5in}
\setlength{\topmargin}{-0.75in}
\setlength{\textwidth}{7in}
\setlength{\topskip}{0in}
\setlength{\oddsidemargin}{-0.5in}
\setlength{\evensidemargin}{-0.5in}
%-----------------------------------------------------------
%\usepackage{fullpage}
\usepackage{shading}
%\textheight=9.0in
\pagestyle{empty}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item[--] #1 \vspace{-4pt}}
\newcommand{\resheading}[1]{{\large \parashade[.9]{sharpcorners}{\textbf{#1 \vphantom{p\^{E}}}}}}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
	\textbf{#1} & \textit{#2} \\
	\textit{#3} & \textit{#4}\\
\end{tabular*}\vspace{-6pt}}


\newcommand{\ressubhead}[2]{
\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
	\textbf{#1} & \textit{#2} \\
\end{tabular*}\vspace{-6pt}}

\usepackage{xcolor}
\usepackage[colorlinks = true, 
	linkcolor = blue,
	urlcolor  = blue,
	citecolor = blue,
	anchorcolor = blue]{hyperref}

\newcommand{\MYhref}[3][blue]{\href{#2}{\color{#1}{#3}}}%

%-----------------------------------------------------------


\begin{document}

\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
	\textbf{\Large Skanda Koppula}  & \href{mailto:skoppula@mit.edu}{skoppula@mit.edu}\\
450 Memorial Drive &  \href{http://github.com/skoppula}{github.com/skoppula}\\
	Cambridge, MA 02139 & 1.412.259.3123\\
\end{tabular*}
\\

\vspace{0.1in}

%\resheading{Education}
\ressubheading{Massachusetts Institute of Technology}{}{\vspace{4mm}Major: Computer Science and Engineering}{Candidate for BSc, 2017}
\textit{Relevant courses:} Constructive Multicore Architecture, Artificial Intelligence, Software Architecture, Design and Analysis of Algorithms, Biostatistics and Genetics, Machine Learning, Computation Structures

\vspace{0.2in}

\large \textbf{Projects and Work Experience\vspace{2mm}} \normalsize
\ressubhead{vuPoint, \textit{a collaborative platform for text comparison}}{Oct. 2013, Aug. 2014}

	\begin{itemize}
		\resitem{HackMIT web project (\href{http://vupoint.meteor.com}{vupoint.meteor.com}) later extended to be a prototype Android app}
		\resitem{Implemented Latent Dirichlet and Gaussian SVMs (via OpenCV) for sentiment and keyword analysis in pairwise essay comparison}
	\end{itemize}

\vspace{0.05in}

	\ressubheading{Structure-Based Statistical Modeling of Protein Interactions}{May 2014 - Aug. 2014}{Informatics Intern at the Keating Lab}{}
	\begin{itemize}
		\resitem{Co-developed five-term frequency-analysis procedure to predict the stability of protein complexes}
		\resitem{Achieved $>350$\% speed-up via algorithmic changes (e.g. developing pre-processed libraries) and extending rate-limiting Python sections with C}
		\resitem{Submitting to \textit{PLoS Computational Biology, Software}}
	\end{itemize}

\vspace{0.05in}

	\ressubheading{Bayesian-Based Prognostic Modeling of Genetic Diseases}{Jan 2013 - Oct. 2013}{Research Student at CSAIL's Biomedical Cybernetics Lab}{}
	\begin{itemize}
			\resitem{Built Bayesian procedure to predict the onset of alcoholism and lung cancer ($\overline{AUC} =0.84$)}
		\resitem{Presented at Am. Medical Informatics Assoc. San Fran 2013. Published in AMIA Proceedings}
	\end{itemize}

\vspace{0.05in}

\ressubheading{CollegeZen, \textit{Pittsburgh-based startup}}{June 2013 - July. 2013}{Data Analysis Intern}{}
	\begin{itemize}
		\resitem{Scripted a web scraping procedure that populated CollegeZen databases with US college profiles}
		\resitem{Prototyped recommendation engine to suggest colleges that students might be interested in}
	\end{itemize}

\vspace{0.1in}
\large \textbf{Skills\vspace{2mm}} \normalsize
	 \begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
		 \hspace{2mm} -- Proficient in \textbf{Java} and \textbf{Python} \\
		 \hspace{2mm} -- Working knowledge of \textbf{C++, R, Javascript, shell scripting, HTML5, Less}, and \textbf{\LaTeX}\\
		 \hspace{2mm} -- Hacked together projects in \textbf{Android} SDK 21.1.0+\\
		 \hspace{2mm} -- Done data visualization with \textbf{Processing} (Java-based graphics language)\\
		 \hspace{2mm} -- Beginning \textbf{Bluespec} (functional hardware design language)\\
	\end{tabular*}

\vspace{0.1in}
\large \textbf{Awards\vspace{2mm}} \normalsize
	 \begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
		 \hspace{2mm} Top Ten in Newbie Division in MIT Battlecode AI Competition & 2014\\
		 \hspace{2mm} Silver Medalist in the USA Mathematics Talent Search & 2013\\
		 \hspace{2mm} First Place Undergrad Research Poster - NSF TeraGrid Supercomputing Conference & 2012\\
		 \hspace{2mm} Finalist in the Google International Science Fair & 2011\\
	\end{tabular*}

\vspace{0.1in}
\large \textbf{Other interests!\vspace{1mm}} \normalsize 
\begin{center}Check out more at my coding, technology, and art blog! \href{http://www.skoppula.github.io}{skoppula.github.io} \end{center} 
\hspace{2mm} -- Doing TopCoder, Project Euler, and USACO problems \\
\hspace{2mm} -- Building electric vehicles (currently a mini-motorcycle!) \\
\hspace{2mm} -- Teaching: \textit{Applied Algorithms in a Romantic World}, \textit{Biochemistry - Kitchen Edition} among others! \\ 
\hspace{2mm} -- Helping out run EECScon, MIT's EECS research conference \\

\end{document}
