
\documentclass[letterpaper,11pt]{article}

%-----------------------------------------------------------
%Margin setup

\setlength{\voffset}{0.1in}
\setlength{\paperwidth}{8.5in}
\setlength{\paperheight}{11in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\textheight}{11in}
\setlength{\textheight}{9.5in}
\setlength{\topmargin}{-0.35in}
\setlength{\textwidth}{7in}
\setlength{\topskip}{0in}
\setlength{\oddsidemargin}{-0.35in}
\setlength{\evensidemargin}{-0.35in}
%-----------------------------------------------------------
%\usepackage{fullpage}
%\textheight=9.0in
\pagestyle{empty}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item[--] #1 \vspace{-4pt}}
\newcommand{\resheading}[1]{{\large \parashade[.9]{sharpcorners}{\textbf{#1 \vphantom{p\^{E}}}}}}
\newcommand{\ressubheading}[4] {
\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
	\textbf{#1} & \textit{#2} \\
	\textit{#3} & \textit{#4}\\
\end{tabular*}\vspace{-6pt}}

\newcommand{\ressubheadingtwo}[2] {
\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
	\textbf{#1} & \textit{#2} \\
\end{tabular*}\vspace{-6pt}}

\newcommand{\ressubhead}[2] {
\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
	\textbf{#1} & \textit{#2} \\
\vspace{0.01in}
\end{tabular*}\vspace{-6pt}}

\usepackage{xcolor}
\usepackage[colorlinks = true, 
	linkcolor = blue,
	urlcolor  = blue,
	citecolor = blue,
	anchorcolor = blue]{hyperref}

\newcommand{\MYhref}[3][blue]{\href{#2}{\color{#1}{#3}}}%

%-----------------------------------------------------------


\begin{document}

\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Skanda Koppula}  & \href{mailto:skoppula@mit.edu}{\nolinkurl{me@skoppula.com}}\\
  Kingly Building, 18 Woodberry Down &  \href{http://skoppula.github.io}{\nolinkurl{skoppula.github.io}}\\
	London, UK N42GQ & +1-412-259-3123\\
\end{tabular*}
\\

\vspace{3mm}

\large \textbf{Work Experience\vspace{1mm}} \normalsize

    \ressubheadingtwo{Google DeepMind, Research Engineer}{September 2018 - Present}
	\begin{itemize}
	        \vspace{-1mm}
            \resitem{Pushing forward research on large-scale visual representation learning, self-supervised learning objectives, and new architectures for dense visual tasks such as object detection, segmentation, and optical flow.}
    \end{itemize}
    \vspace{1mm}

    \ressubheadingtwo{NVIDIA Autonomy, PilotNet Team, Intern}{May 2018 - September 2018}
	\begin{itemize}
	        \vspace{-1mm}
            \resitem{Added support for multi-camera vehicle feeds on the PilotNet training and simulation pipelines.}
            \vspace{-1.5mm}
            \resitem{Decreased training time by 16\% using custom data format to reduce disk reads and CRC overhead.}
	\end{itemize}

	\ressubheadingtwo{Google Acoustic Modeling Team, Intern}{June 2017 - September 2017}
	\begin{itemize}
	        \vspace{-1mm}
            \resitem{Developed approach to characterize and visualize the memory contents and hidden state of recurrent neural networks used in character language models. Work published in ICASSP 2018.}
            \vspace{-1.5mm}
            \resitem{Tested kernel factorization as a way to improve cross-domain accuracy of neural language models.}
	\end{itemize}

	\ressubheadingtwo{Yahoo Login Team, Intern}{June 2016 - August 2016}
	\begin{itemize}
	        \vspace{-1mm}
            \resitem{Improved malicious login attempt detection by 7\% using low-latency, quantized neural networks.}
            \vspace{-1.5mm}
            \resitem{Implemented online updating of the login classifier by pulling live data from external feed.}
	\end{itemize}

    \vspace{0.02in}
	\ressubheadingtwo{Square Security, Intern}{June 2015 - Aug. 2015}
	\begin{itemize}
	        \vspace{-1mm}
            \resitem{Built an in-production service to collect memory dumps from Square card readers.}
            \vspace{-1.5mm}
            \resitem{Simplified firmware bug-fixing by parsing dumps into a human readable source error trace.}
	\end{itemize}

    \vspace{0.05in}

\vspace{0.05in}


\large \textbf{Projects\vspace{1mm}} \normalsize

    \ressubheadingtwo{ETH Z{\"u}rich, Fulbright Research Fellowship, Researcher}{Sept. 2018 - June 2019}{}
	\begin{itemize}
	        \vspace{-1mm}
            \resitem{Developed CNN fine-tuning procedure to improve bit error resilience. Paired with approximate DRAM modules (voltage and timing scaled), this yielded a 29\% power reduction and 5\% speed-up while running inference on state-of-art CNNs on CPU, GPU, and state-of-art neural accelerators.}
	\end{itemize}

	\ressubheadingtwo{MIT Energy Efficient Systems Lab, Master's Thesis}{Sept. 2016 - 2018}{}
	\begin{itemize}
	        \vspace{-1mm}
            \resitem{Achieved a \textgreater 2x speed-up and \textgreater500x decrease in estimated energy consumption for real-time speaker identification by demonstrating a quantized speaker ID neural network and an FPGA design capable of neural network inferencing and mel-frequency coefficient extraction.}
	\end{itemize}

    \ressubheadingtwo{MIT Formula Student Driverless, Team Co-Founder}{September 2017 - March 2019}
    \begin{itemize}
        \vspace{-1mm}
        \resitem{Helped hire and manage new recruits for a team that built the entire autonomy stack of a Formula Student racecar. Closely directed technical efforts on the perception team, demonstrating an accurate LiDAR-stereo camera system for racetrack landmark localization.}
        \vspace{-1mm}
        \resitem{Won 2nd and 3rd place at the 2019 Formula Student Driverless Italy and Germany competitions.}
    \end{itemize}

    \ressubheadingtwo{MIT Formula SAE Racecar Team, Member}{September 2015 - 2017}
    \begin{itemize}
        \resitem{Developed PCBs and firmware for an open-source automotive battery management system. Orchestrated battery dis/charging state, balancing, safety checks, and charging algorithms.}
        \resitem{Won 2nd place at the 2017 U.S. Formula Student Electric competition (among 23 teams).}
    \end{itemize}

\vspace{0.1in}

\large \textbf{Education\vspace{2mm}} \normalsize
\ressubheading{Massachusetts Institute of Technology}{}{\vspace{4mm}Masters of Engineering and BSc, Computer Systems,  MEng GPA: 5.0/5.0}{Sept. 2013 - June 2018}
\textit{Relevant courses:} Digital Architectures for Deep Learning, Applied Cryptography, Compilers, Machine Learning, Operating Systems, Computer Networks and Security, Bayesian Inference 

\vspace{0.1in}


%     \ressubheadingtwo{Power-Based Side-Channel Attack on ATMega328}{Nov. 2015}{}
% 	\begin{itemize}
%             \resitem{Demonstrated extraction of an AES key from an Arduino's flash memory from chip's power traces. Implemented the Correlation Power Analysis attack.}
% 	\end{itemize}

%     \ressubheadingtwo{Bayesian Inference for Detection of Illness Pre-disposition}{May 2013}{}
% 	\begin{itemize}
%             \resitem{Applied Bayesian modeling to develop a genomic-environmental factor model to detect patients at-risk or pre-disposed to cancer, schizophrenia, and alcoholism. Published in AMIA 2014: \url{https://www.ncbi.nlm.nih.gov/pubmed/24303313}}
% 	\end{itemize}

    \vspace{0.05in}

\large \textbf{Skills\vspace{1mm}} \normalsize
	 \begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
	     \hspace{2mm} Software: \textbf{Python} (including \textbf{Tensorflow}, \textbf{PyTorch}, \textbf{Jax}, \textbf{numpy}), \textbf{Java}, \textbf{Scala}, \textbf{C++}, \textbf{bash}  \\
         \hspace{2mm} Embedded Systems and Digital Design: \textbf{C}, \textbf{Altium}, \textbf{Vivado HLS}, and \textbf{Bluespec Verilog}. \\
         
	\end{tabular*}

\vspace{0.2in}

\large \textbf{Research Publications\vspace{1mm}} \normalsize
    \vspace{0.05in}

\textbf{Perceiver IO: A General Architecture for Structured Inputs \& Outputs}. \\
\textit{International Conference on Learning Representations (ICLR) 2022}. \\
Andrew Jaegle, Sebastian Borgeaud, Jean-Baptiste Alayrac, Carl Doersch, Catalin Ionescu, David Ding, \textbf{Skanda Koppula}, Daniel Zoran, Andrew Brock, Evan Shelhamer, Olivier Hénaff, Matthew M. Botvinick, Andrew Zisserman, Oriol Vinyals, João Carreira.

\vspace{0.1in}

\textbf{Efficient Visual Pretraining with Contrastive Detection}. \\
\textit{International Conference on Computer Vision (ICCV 2021), Oral}. \\
Olivier J. Henaff, \textbf{Skanda Koppula}, Jean-Baptiste Alayrac, Aaron van den Oord, Oriol Vinyals, Joao Carreira

\vspace{0.1in}

\textbf{A Deep Learning Approach for Characterizing Major Galaxy Mergers}. \\
\textit{NeurIPS 2020 Workshop: ML for Physical Science (NeurIPS ML4PS 2020)}. \\
\textbf{Skanda Koppula}, Victor Bapst, Marc Huertas-Company, Sam Blackwell, Agnieszka Grabska-Barwinska, Sander Dieleman, 
Andrea Huber, Natasha Antropova, Mikolaj Binkowski, Hannah Openshaw, Adria Recasens, Fernando Caro, Avishai Dekel, Yohan Dubois, Jesus Vega Ferrero, David C. Koo1, Joel R. Primack, Trevor Back

\vspace{0.1in}

\textbf{Accurate, Low-Latency Visual Perception for Autonomous Racing: Challenges, Mechanisms, and Practical Solutions}. \\
\textit{The IEEE/RSJ International Conference on Intelligent Robots and Systems (IROS 2020)}. \\
Kieran Strobel, Sibo Zhu, Raphael Chang, and \textbf{Skanda Koppula}

\vspace{0.1in}

\textbf{EDEN: Enabling Energy-Efficient, High-Performance Deep Neural Network Inference Using Approximate DRAM}. \\
\textit{The 52nd Annual IEEE/ACM International Symposium on Microarchitecture (MICRO 2019)}. \\
\textbf{Skanda Koppula}, Lois Orosa, A. Giray Yaglicki, Roknoddin Azizi, Taha Shahroodi, Konstantinos Kanellopoulos, and Onur Mutlu

\vspace{0.1in}

\textbf{Understanding Recurrent Neural State Using Memory Signatures}. \\
\textit{2018 IEEE International Conference on Acoustics, Speech and Signal Processing (ICASSP 2018)}. \\
\textbf{Skanda Koppula}, Khe Chai Sim, and Kean Chin

\vspace{0.1in}

\textbf{Energy-Efficient Speaker Identification With Low-Precision Networks}. \\
\textit{2018 IEEE International Conference on Acoustics, Speech and Signal Processing (ICASSP 2018).}. \\
\textbf{Skanda Koppula}, James Glass, and Anantha P. Chandrakasan


\end{document}
