
\documentclass[letterpaper,11pt]{article}

%-----------------------------------------------------------
%Margin setup

\setlength{\voffset}{0.1in}
\setlength{\paperwidth}{8.5in}
\setlength{\paperheight}{11in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\textheight}{11in}
\setlength{\textheight}{9.5in}
\setlength{\topmargin}{-0.35in}
\setlength{\textwidth}{7in}
\setlength{\topskip}{0in}
\setlength{\oddsidemargin}{-0.35in}
\setlength{\evensidemargin}{-0.35in}
%-----------------------------------------------------------
%\usepackage{fullpage}
%\textheight=9.0in
\pagestyle{empty}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item[--] #1 \vspace{-4pt}}
\newcommand{\resheading}[1]{{\large \parashade[.9]{sharpcorners}{\textbf{#1 \vphantom{p\^{E}}}}}}
\newcommand{\ressubheading}[4] {
\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
	\textbf{#1} & \textit{#2} \\
	\textit{#3} & \textit{#4}\\
\end{tabular*}\vspace{-6pt}}

\newcommand{\ressubheadingtwo}[2] {
\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
	\textbf{#1} & \textit{#2} \\
\end{tabular*}\vspace{-6pt}}

\newcommand{\ressubhead}[2] {
\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
	\textbf{#1} & \textit{#2} \\
\vspace{0.01in}
\end{tabular*}\vspace{-6pt}}

\usepackage{xcolor}
\usepackage[colorlinks = true, 
	linkcolor = blue,
	urlcolor  = blue,
	citecolor = blue,
	anchorcolor = blue]{hyperref}

\newcommand{\MYhref}[3][blue]{\href{#2}{\color{#1}{#3}}}%

%-----------------------------------------------------------


\begin{document}

\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Skanda Koppula}  & \href{mailto:skoppula@mit.edu}{\nolinkurl{skoppula@mit.edu}}\\
  550 Memorial Drive &  \href{http://skoppula.github.io}{\nolinkurl{skoppula.github.io}}\\
	Cambridge, MA 02139 & 1.412.259.3123\\
\end{tabular*}
\\

\vspace{0.1in}

%\resheading{Education}
\ressubheading{Massachusetts Institute of Technology}{}{\vspace{4mm}Masters of Engineering, Computer Systems and Security,  GPA: 5.0/5.0}{Expected Dec. 2017}
\ressubheading{Massachusetts Institute of Technology}{}{\vspace{4mm}BSc. Computer Science and Engineering,  GPA: 4.7/5.0}{Sept. 2013 - June 2016}
\textit{Relevant courses:} Advanced Machine and Statistical Learning, Computer and Network Security, Applied Cryptography, Compilers, Operating Systems, Design and Analysis of Algorithms (Teaching Assistant), Theory of Computation, Computer Architecture, Computer Networks, Bayesian Inference 

\vspace{0.2in}

\large \textbf{Work Experience\vspace{3mm}} \normalsize

	\ressubheadingtwo{Google Search, Research Intern}{June 2017 - Ongoing}
	\begin{itemize}
            \resitem{Demonstrated decomposition methods to improve cross-domain adaptability of neural language models (LSTM/RNNs). Currently experimenting with decoding of LSTM memory state to improve interpretability of language models. }
	\end{itemize}

	\ressubheadingtwo{Yahoo Login Abuse Team, Software Engineering Intern}{June 2016 - Sep. 2016}
	\begin{itemize}
            \resitem{Prototyped DNN to recognize spam login events, realizing a 6\% decrease in error rate. }
		    \resitem{Deployed parallelized data feed to pull data hourly from 31 sources, updating production classifier.}
	\end{itemize}

    \vspace{0.05in}
	\ressubheadingtwo{Square Security Infrastructure Team, Software Engineering Intern}{June 2015 - Aug. 2015}
	\begin{itemize}
            \resitem{Developed service to collect memory core crashdumps from Square card readers, symbolifing the binary contents to a human-readable source error trace.}
	\end{itemize}

    \vspace{0.05in}

\large \textbf{Selected Projects\vspace{3mm}} \normalsize
    \vspace{0.05in}

	\ressubheadingtwo{MIT Energy Efficient Circuits Group}{Sept. 2015 - Present}{}
	\begin{itemize}
            \resitem{Developed memory-efficient LSTM/DNN neural network to replace traditional i-vector system for speaker verification. 3x reduction in model size. Prototyped FPGA with on-chip BRAM model}
	\end{itemize}

    \vspace{0.05in}
	\ressubheadingtwo{MIT Formula SAE Team, Software Lead}{August 2015 - Present}
	\begin{itemize}
            \resitem{Designed and produced firmware for the first open-source automotive battery management system. Orchestrates battery dis/charging state, balancing, safety checks, charging algorithms. \url{https://github.com/MITEVT/ltc-battery-controller}}
		\resitem{Developed team's CAN and SPI firmware libraries for 32-bit ARM microcontrollers, enabling intra-vehicle electronics communications.}
        \resitem{Car won 2nd Place at North American FSAE Lincoln Electric Racing Competition.}
	\end{itemize}

    \vspace{0.05in}
	\ressubheadingtwo{MIT 6.035 Compiler Final Project}{May 2016}
	\begin{itemize}
            \resitem{With team, built a complete compiler (parser to assembly) for Decaf, a C-like language. Additionally, implemented various loop and threading optimization.}
	\end{itemize}

    \vspace{0.05in}

\large \textbf{Selected Research \vspace{3mm}} \normalsize
    \ressubheadingtwo{Power-Based Side-Channel Attack on ATMega328}{Nov. 2015}{}
	\begin{itemize}
            \resitem{Demonstrated extraction of an AES key from an Arduino's flash memory from chip's power traces}
            \resitem{Built hardware setup to measure power consumption, and implemented the Correlation Power Analysis attack.}
	\end{itemize}
    \vspace{0.2in}
    \ressubheadingtwo{Bayesian Inference for Detection of Alcoholism Pre-disposition}{May 2013}{}
	\begin{itemize}
            \resitem{Applied Bayesian modeling to develop a genomic-environmental factor model to detect patients at-risk or pre-disposed to alcoholism}
            \resitem{Published in Proceedings of the American Medical Informatics Association.}
            \resitem{Available at \url{https://www.ncbi.nlm.nih.gov/pubmed/24303313}}
	\end{itemize}

\large \textbf{Skills\vspace{2mm}} \normalsize
	 \begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
         \hspace{2mm} Embedded Systems: \textbf{C}, \textbf{x86 Assembly}, \textbf{Vivado HLS}, and \textbf{Bluespec Verilog}. \\
         \hspace{2mm} Misc: \textbf{Python}, \textbf{Java}, \textbf{Scala}, \textbf{shell}, \textbf{TensorFlow}  \\
         \hspace{2mm} Web Systems: \textbf{JAX-RS/Jetty}, \textbf{Rails/RSpec}, \textbf{Flask} \\
	\end{tabular*}

\vspace{0.1in}
\large \textbf{Awards\vspace{2mm}} \normalsize
	 \begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
		 \hspace{2mm} Cisco Snort Security Scholarship Recipient & 2017\\
		 \hspace{2mm} Analog Devices Research and Innovation Scholar Award & 2016\\
		 \hspace{2mm} Top Research Poster at the 2016 MIT EECSCon Undergraduate Research Conference & 2016\\
		 \hspace{2mm} Third Place in Jane Street Collegiate Programmatic Trading Competition & 2015\\
	\end{tabular*}
\end{document}
